---
title: "bond_lab03"
format: html
editor: visual
---

```{r}
library(tidyverse)
bond.data <- read_csv("data/jamesbond.csv")
bond.data
```

# Which movie earned the **most**?

```{r}
bond.data |>
    select(Year, Movie, US_Gross) |>
    arrange(desc(US_Gross))
```

The most profitable movie was Skyfall, made in 2012. It made a profit of about \$300 million.

# Is there a correlation between budget and earnings?

```{r}
ggplot(bond.data, aes(x=Budget, y=US_Gross)) +
    geom_point()
```

# This doesn't account for inflation. Check: add colours for year?

```{r}
ggplot(bond.data, aes(x=Budget, y=US_Gross, color=Year)) +
    geom_point() +
    scale_color_continuous()
```

Definitely looks like year correlates with both earnings and budget. The dataset contains inflation-adjusted numbers, let's use those instead.

```{r}
ggplot(bond.data, aes(x=Budget_Adj, y=US_Adj, color=Year)) +
    geom_point() +
    scale_color_continuous()
```

Still seems budget is increasing with year even after inflation adjustment, but the correlation with returns is now much less clear.

# Just for fun: is there a correlation between the number of times Bond says "Bond, James Bond" and return??

```{r}
ggplot(bond.data, aes(x=BJB, y=US_Adj)) +
    geom_point() +
    scale_color_continuous()
```

It seems the movies earn more if he says it 0 or 2 times? Probably a spurious correlation!
```{r}
ggplot(bond.data, aes(x=Bond, y=US_Adj))+
  geom_point(colour="purple")
```

